A mechanical Model of Rod-Shaped Bacteria

### 2025-01-29 paper/main.tex
use tikzonimage to refine figures

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.3\textwidth]
        {../docs/source/_static/09395645494836445480/raw_pv/000000400.png}
        \node at (0.1, 0.9)[anchor=north west, rectangle, draw, white, minimum width=20pt, minimum height=20pt]{a)};
    \end{tikzonimage}
    \includegraphics[width=0.3\textwidth]
        {../docs/source/_static/09395645494836445480/images/000000400.png}
    \includegraphics[width=0.3\textwidth]
        {../docs/source/_static/09395645494836445480/masks/000000400.png}
    \caption{Snapshots at \dots}
    \label{fig:progression-image-generation}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.3\textwidth]
        {../docs/source/_static/fitting-methods/progressions-1.png}
    \includegraphics[width=0.3\textwidth]
        {../docs/source/_static/fitting-methods/progressions-2.png}
    \linebreak
    \includegraphics[width=0.3\textwidth]
        {../docs/source/_static/fitting-methods/progressions-3.png}
    \includegraphics[width=0.3\textwidth]
        {../docs/source/_static/fitting-methods/progressions-4.png}
    \caption{1}
    \label{fig:mask-difference-metric}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.32\textwidth]
        {../docs/source/_static/fitting-methods/extract_positions-000400.png}
    \includegraphics[width=0.32\textwidth]
        {../docs/source/_static/fitting-methods/extract_positions-000600.png}
    \includegraphics[width=0.32\textwidth]
        {../docs/source/_static/fitting-methods/extract_positions-001200.png}
    \caption{Progression of generated masks with estimated and exact positions.}
    \label{fig:position-extraction}
\end{figure}

>>>>

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.3\textwidth]
        {../docs/source/_static/09395645494836445480/raw_pv/000000400.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{a}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.3\textwidth]
        {../docs/source/_static/09395645494836445480/images/000000400.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{b}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.3\textwidth]
        {../docs/source/_static/09395645494836445480/masks/000000400.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{c}};
    \end{tikzonimage}
    \caption{Snapshots at \dots}
    \label{fig:progression-image-generation}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.32\textwidth]
        {../docs/source/_static/fitting-methods/algorithm/image001042.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{a}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {../docs/source/_static/fitting-methods/algorithm/mask-zoom.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{b}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {../docs/source/_static/fitting-methods/algorithm/mask-zoom.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{c}};
    \end{tikzonimage}
    \caption{}
    \label{fig:position-extraction-algorithm}
\end{figure}

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.32\textwidth]
        {../docs/source/_static/fitting-methods/extract_positions-000400.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{a}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {../docs/source/_static/fitting-methods/extract_positions-000600.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{b}};
    \end{tikzonimage}
    \begin{tikzonimage}[width=0.32\textwidth]
        {../docs/source/_static/fitting-methods/extract_positions-001200.png}
        \node at (0.025, 0.975)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{c}};
    \end{tikzonimage}
    \caption{Progression of generated masks with estimated and exact positions.}
    \label{fig:position-extraction}
\end{figure}
